Light inextensible strings under tension in the Schwarzschild geometry

### 2018-10-01 string_longer_document.tex
add the longer paper

\begin{abstract}
Here I analyze the behaviour of light inextensible strings under
tension in the vicinity of a black hole.  Proper length (given by the
spatial component of the Schwarzshild metric) is minimized by the
Euler-Lagrange equations.  Light inextensible taut strings may assume
a range of distinct configurations with an arbitrarily high winding
number around the central singularity, and here I give a range of
numerical solutions and theoretical observations.
\end{abstract}

@@

Figure~\ref{closest_approach_non_self_intersecting} shows
nonselfintersecting strings indexed by distance of approach to the
singularity, which occurs at~$\phi=0$.  Strings with a sufficiently
close passage to the event horizon self-intersect; numerical methods
show that the critical value is~$\simeq 1.076109317$, with an
uncertainty of 1 in the last digit: if a string with two free ends
passes closer than this, it forms a closed loop.
Figure~\ref{closest_approach_non_self_intersecting} shows some
non-self-intersecting strings and
figure~\ref{closest_approach_self_intersecting} shows some strings
that self-intersect.

>>>>

\begin{abstract}

\end{abstract}

@@

Figure~\ref{closest_approach_non_self_intersecting} shows
nonselfintersecting strings indexed by distance of approach to the
singularity, which occurs at~$\phi=0$.  Strings with a sufficiently
close passage to the event horizon self-intersect; numerical methods
show that the critical value is~$\simeq 1.076109317$, with an
uncertainty of 1 in the last digit: if a string with two free ends
passes closer than this to the event horizon,
Figure~\ref{closest_approach_non_self_intersecting} shows some
non-self-intersecting strings and
figure~\ref{closest_approach_self_intersecting} shows some strings
that self-intersect.
